---
title: "Pacific Island to National standards comparisons"
author: "Todd-Brown, Katherine"
date: "2024-02-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 327

```{sh}
diff data_lvl02/327_Conservation_Cover_PI_CPS_2016.yaml data_lvl02/327_Conservation_Cover_NHCP_CPS_2014.yml > data_lvl03/327_compare.log
```

## CSP 380 Windbreak

```{sh}
diff data_lvl02/380_Windbreak_Shelterbelt_Establishment_NHCP_CPS_2021.yaml data_lvl02/380_Windbreak_Shelterbelt_Establishment_PIA_CPS_2022.yaml > data_lvl03/380_compare.log
```

```{r}
NHCP380 <- read_yaml('data_lvl02/380_Windbreak_Shelterbelt_Establishment_NHCP_CPS_2021.yaml')
PIA380 <- read_yaml('data_lvl02/380_Windbreak_Shelterbelt_Establishment_PIA_CPS_2022.yaml')

```


## CSP 379 Forest Farming

```{sh}
diff data_lvl02/379_Forest_Farming_NHCP_CPS_2020.yaml data_lvl02/379_Forest_Farming_PIA_CPS_2023.yaml > data_lvl03/379_compare.log
```

```{r}
PIA380 <- read_yaml('data_lvl02/380_Windbreak_Shelterbelt_Establishment_PIA_CPS_2022.yaml')

NHCP380 <- read_yaml('data_lvl02/380_Windbreak_Shelterbelt_Establishment_NHCP_CPS_2021.yaml')

#base::intersect(PIA380, NHCP380)
```

## CSP 612 Tree Shrub Establishment

```{sh}
diff data_lvl02/612_Tree_Shrub_Establishment_NHCP_CPS_2022.yaml data_lvl02/612_Tree_Shrub_Establishment_PI_CPS_2017.yaml > data_lvl03/612_compare.log
```

```{r}
PIA612 <- read_yaml('data_lvl02/612_Tree_Shrub_Establishment_PI_CPS_2017.yaml')

NHCP612 <- read_yaml('data_lvl02/612_Tree_Shrub_Establishment_NHCP_CPS_2022.yaml')

```

### Symantic differences

#### Definition
PI standards allow for "seedlings or cuttings" where as national standard does not.

```{r}
PIA612$definition
NHCP612$definition
```

#### Purpose

PI standards allow for "`r PIA612$purpose[8]`"

All other differences seem to be semantic

```{r}
PIA612$purpose
NHCP612$purpose
```

Conditions are the same.

#### Criteria 

TODO CHECK CRITERIA TO SEE IF THERE ARE SIGNIFICANT DIFFERENCES

```{r}
PIA612$criteia

NHCP612$criteia
```

#### considerations

PI does not have 'Reducing Energy Use' as a possible consideration

TODO CHECK CONSIDEATIONS FOR EFFECTIVE MAPPING

```{r}
PIA612$considerations

NHCP612$considerations
```

## Pending

Mulching 484
Conservation cover 327
Nutrient Management 590

