---
title: "Pacific Island to National standards comparisons"
author: "Todd-Brown, Katherine"
date: "2024-02-09"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(yaml)

knitr::opts_chunk$set(echo = TRUE)
```

# SOIL CARBON AMENDMENT (336)

## Difference

Overall there are there are no differences between standards asside from date of creation.


```{sh eval=FALSE}
diff data_lvl02/336_Soil_Carbon_Amendment_PI_CPS.yml data_lvl02/336_Soil_Carbon_Amendment_NHCP_CPS_2022.yml > data_lvl03/336_compare.log
```

```{r}
cat(paste0(read_lines('data_lvl03/336_compare.log'), collapse = '\n'))
```

# MULCHING (484)

Overall there are there are no significant differences between standards, however there are 5 identified grammatical differences.

```{sh eval=FALSE}
diff data_lvl02/484_Mulching_PI_CPS_2022.yml data_lvl02/484_Mulching_NHCP_CPS_2017.yml > data_lvl03/484_compare.log
```

```{r}
cat(paste0(read_lines('data_lvl03/484_compare.log'), collapse = '\n'))
```

# Brush Management (314)

**Summarize differences**

```{sh eval=FALSE}
diff data_lvl02/314_Brush_Management_PI_CPS_2018.yml data_lvl02/314_Brush_Management_NHCP_CPS_2017.yml > data_lvl03/314_compare.log
```

```{r}
cat(paste0(read_lines('data_lvl03/484_compare.log'), collapse = '\n'))
```


# CONSERVATION COVER (327)

## Differences

Overall there are there are no significant differences between standards with the exception of documentation for plans and specifications.

```{sh eval=FALSE}
diff data_lvl02/327_Conservation_Cover_PI_CPS_2016.yaml data_lvl02/327_Conservation_Cover_NHCP_CPS_2014.yml > data_lvl03/327_compare.log
```

```{r}
cat(paste0(read_lines('data_lvl03/327_compare.log'), collapse = '\n'))
```

# TODO: GRAZING LAND MECHANICAL TREATMENT (548)

Significant line by line differences.

```{sh eval=FALSE}
diff data_lvl02/548_Grazing_Land_Mechanical_Treatment_NHCP_CPS_2022.yml data_lvl02/548_Grazing_Land_Mechanical_Treatment_PI_CPS_2015.yml > data_lvl03/548_compare.log
```

# TODO: WINDBREAK-SHELTERBELT ESTABLISHMENT AND RENOVATION (380)

## Differences

Overall references to snow are removed from Pacific Island specifications, burning is not allowed in Pacific Islands, species are specifications are difference, and restoration is explicitly named in Pacific islands.

```{sh eval=FALSE}
diff data_lvl02/380_Windbreak_Shelterbelt_Establishment_NHCP_CPS_2021.yml data_lvl02/380_Windbreak_Shelterbelt_Establishment_PIA_CPS_2022.yml > data_lvl03/380_compare.log
```

```{r}
#read_yaml('data_lvl02/380_Windbreak_Shelterbelt_Establishment_NHCP_CPS_2021.yml')
#read_yaml('data_lvl02/380_Windbreak_Shelterbelt_Establishment_PIA_CPS_2022.yml')
```

# TODO: 612

```{sh eval=FALSE}
diff data_lvl02/612_Tree_Shrub_Establishment_NHCP_CPS_2022.yml data_lvl02/612_Tree_Shrub_Establishment_PI_CPS_2017.yml > data_lvl03/612_compare.log
```

# TODO: CSP 379 Forest Farming

```{sh eval=FALSE}
diff data_lvl02/379_Forest_Farming_NHCP_CPS_2020.yaml data_lvl02/379_Forest_Farming_PIA_CPS_2023.yaml > data_lvl03/379_compare.log
```

```{r}
PIA380 <- read_yaml('data_lvl02/380_Windbreak_Shelterbelt_Establishment_PIA_CPS_2022.yaml')

NHCP380 <- read_yaml('data_lvl02/380_Windbreak_Shelterbelt_Establishment_NHCP_CPS_2021.yaml')

#base::intersect(PIA380, NHCP380)
```

